Cover Letter

### 2021-09-21 paper/latex/NetworkNeuroscience/cover_letter.tex
tweaks

\begin{document}
\bibliographystyle{plain}
\thispagestyle{fancy}
% \addtolength{\topmargin}{-63.87003pt}
\setlength{\headheight}{30.0pt}
\fancyhead[C]{\includegraphics[height=0.5in]{stfx_text.png}}
\fancyhead[L]{\includegraphics[height=0.5in]{crest.png}}
\fancyhead[R]{
    \sffamily
    \scriptsize
    4130 University Avenue \\
    B2G 2W5 \\
    Antigonish, Nova Scotia \\
    Canada
}
\normalsize

@@

Numerous fMRI studies examine correlations amongst regions of interest (ROI) in the brain. These
``functional connectivity'' analyses typically use ROIs or seed regions in order to simplify
connectivity computations \citep{huettelFunctionalMagneticResonance2004}. Instead, we use
statistics from RMT to summarize \emph{all} voxelwise correlations with no reductions. In
addition, rather than simply reporting findings which are statistically significant, we report all
analyses from a cross-validated predictive framework, where multiple machine learnign models are
compared against both each other and proper baselines (e.g. niave / dummy classifiers).

We show that, across a variety of data and with fairly small data, and without any model tuning,
that these RMT reductions have real predictive utility and potential. This suggests RMT has
potential as a powerful method for summarizing functional connectivity information. As much of the
research in network neuroscience involves fMRI, functional connectivity, and statistical physics, as
per the \href{https://direct.mit.edu/netn/pages/submission-guidelines#aims}{Aims and Scope} of \emph{Network
Neuroscience}, we believe our manuscript to be an excellent fit for submission to your journal.

This paper is not under consideration at any other journal, although a poster of some preliminary
results of our study was presented at the International Symposium for Magnetic Resonance in Medicine
2021 annual conference \citep{bergerOpenSourceRandom2021}. Our lab has REB ethics approval for
conducting retrospective analyses, although we are unaware of the need for this, this being an
analysis of anonymized public data. All authors approve the manuscript in its submitted form, and
have no conflicts of interest, financial or otherwise. Should you consider to review our manuscript,
we have suggested a number of potential reviewers on your submission website that we believe would
be suitable due to expertise in RMT and similar interdisciplinary research:

>>>>

\begin{document}
\bibliographystyle{plain}
\fancypagestyle{nofooter}{\fancyfoot{}}
\thispagestyle{nofooter}  %  https://tex.stackexchange.com/questions/136384/remove-footer-without-removing-the-header
\setlength{\headheight}{30.0pt}
\fancyhead[C]{\includegraphics[height=0.5in]{stfx_text.png}}
\fancyhead[L]{\includegraphics[height=0.5in]{crest.png}}
\fancyhead[R]{
    \sffamily
    \scriptsize
    4130 University Avenue \\
    B2G 2W5 \\
    Antigonish, Nova Scotia \\
    Canada
}
\normalsize

@@

Numerous fMRI studies examine correlations amongst regions of interest (ROI) in the brain. These
``functional connectivity'' analyses typically use ROIs or seed regions in order to simplify
connectivity computations \citep{huettelFunctionalMagneticResonance2004}. Instead, we use
statistics from RMT to summarize \emph{all} voxelwise correlations with no reductions. In
addition, rather than simply reporting findings which are statistically significant, we report all
analyses from a cross-validated predictive framework, where multiple machine learning models are
compared against both each other and proper baselines (e.g. naive / dummy classifiers).

We show that, across a variety of data and with fairly small data, and without any model tuning,
that these RMT reductions have real predictive utility and potential. This suggests RMT could
be a powerful and efficient method for summarizing functional connectivity information. As much of the
research in network neuroscience involves fMRI, functional connectivity, and statistical physics, as
per the \href{https://direct.mit.edu/netn/pages/submission-guidelines#aims}{Aims and Scope} of \emph{Network
Neuroscience}, we believe our manuscript to be an excellent fit for submission to your journal.

Should you consider to review our manuscript, we have suggested a number of potential reviewers on
your submission website that we believe would be suitable due to expertise in RMT and similar
interdisciplinary research. This paper is not under consideration at any other journal (although a
poster of some preliminary results of our study was presented at the International Symposium for
Magnetic Resonance in Medicine 2021 annual conference \citep{bergerOpenSourceRandom2021}). Our lab
has REB ethics approval for conducting retrospective analyses (although we are unaware of the need,
this being an analysis of anonymized public data). All authors approve the manuscript in its
submitted form, and have no conflicts of interest, financial or otherwise.
